Clean 2015 Raw Data

### 2018-04-26 data-raw/README.Rmd
Add Table 1
Split N_rates into own data
Generate `tibble` object of N rates ad timing in "/data-raw"

Include `N_rates` as a `tibble` object

Document `N_rates`

Update static docs
Update N_rates data frame

>>>>

# N rates

Create a `tibble` of N rates and time of application used in this study.

```{r N_rates}

Year <- as.integer(c(2015,
                     2015,
                     2015,
                     2016,
                     2016))

`Total N (kg/ha)` <- as.integer(c(0,
                                  100,
                                  120,
                                  60,
                                  180))

`Basal N (kg/ha)` <- as.integer(c(0,
                                  60,
                                  60,
                                  30,
                                  60))

`Tillering N (kg/ha)` <- as.integer(c(0,
                                      20,
                                      30,
                                      30,
                                      60))

`Panicle Initiation N (kg/ha)` <- as.integer(c(0,
                                               20,
                                               30,
                                               0,
                                               60))

N_rates <- cbind(Year,
                 `Total N (kg/ha)`,
                 `Basal N (kg/ha)`,
                 `Tillering N (kg/ha)`,
                 `Panicle Initiation N (kg/ha)`)

row.names(N_rates) <- c("N0", "N100", "N120", "N60", "N180")

devtools::use_data(N_rates,
                   compress = "bzip2",
                   overwrite = TRUE)
```
